---
title: "Data 607 Assignment 9"
author: "Coco Donovan"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

## Introduction

I chose to use The New York Times "Most Popular API," with a focus on the last 
30 days (from [insert date]). I have limited experience working with API's up 
until this point, so this will serve as a great opportunity to get my feet wet.
I will also try to document quagmire's that come up during this assignment.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading the necessary packages

```{r}
library(httr)
library(jsonlite)
library(dplyr)
```

Note: For whatever reason, when I loaded jsonlite and tried to run the code
without "jsonlite::" in front of "fromJSON," the code did not work. I would love to 
understand why this was the case.

```{r}
url <- 'https://api.nytimes.com/svc/mostpopular/v2/viewed/30.json?api-key=jBvT5e5Dn4qZTbHgmdS9volt2ddGQIII'

json <- jsonlite::fromJSON(url)
```



```{r}
most_pop <- json$results
```

## Printing the head of the data

```{r}
head(most_pop)
```

Note: What would have been cool is if the data included a view count, but it 
does not seem like that is the case.

```{r}
most_pop_sections <- most_pop %>%
  select('section') %>%
  group_by(section) %>%
  summarize(percent = 100 * n()/nrow(.)) %>%
  arrange(desc(percent))

knitr::kable(most_pop_sections)
```

## Conclusion

Within the twenty most popular articles in the past 30 days, it seems that by 
far and away the most popular article section is the "U.S." section. Now this 
analysis only pertains to the last 30 days and so this popularity may change, 
but I would guess that with increasingly polarized politics, this section 
viewership may not change all that much.
